\sysfull

### 2018-08-07 paper/asplos19/systemdescription.tex
System description revised

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the modified pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} outlines VMM.

>>>>

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} outlines VMM.
